\chapter{Introduction}
\label{chapter: introduction}

A single column model (SCM) can be a valuable tool for diagnosing the performance of a physics suite, from validating that schemes have been integrated into a suite correctly to deep dives into how physical processes are being represented by the approximating code. This SCM has the advantage of working with the Common Community Physics Package (CCPP), a library of physical parameterizations for atmospheric numerical models and the associated framework for connecting potentially any atmospheric model to physics suites constructed from its member parameterizations. In fact, this SCM serves as perhaps the simplest example for using the CCPP and its framework in an atmospheric model. This version contains all parameterizations of NOAA's evolved operational GFS v16 suite (implemented in 2021), plus additional developmental schemes. The schemes are grouped in six supported suites described in detail in the \href{https://dtcenter.ucar.edu/GMTB/v6.0.0/sci_doc/}{CCPP Scientific Documentation} (GFS\_v16, GFS\_v17p8, RAP, HRRR, and RRFS\_v1beta, and WoFS\_v0).

This document serves as both the User and Technical Guides for this model. It contains a Quick Start Guide with instructions for obtaining the code, compiling, and running a sample test case, an explanation for what is included in the repository, a brief description of the operation of the model, a description of how cases are set up and run, and finally, an explanation for how the model interfaces with physics through the CCPP infrastructure.

Please refer to the release web page for further documentation and user notes:\\ \url{https://dtcenter.org/community-code/common-community-physics-package-ccpp/download}

\section{Version Notes}

The CCPP SCM v6.0.0 contains the following major and minor changes since v5.0.

Major
\begin{itemize}
\item Inclusion of regression testing functionality
\item Combine single- and multi-run capabilities into one script
\end{itemize}

Minor
\begin{itemize}
\item Add RUC LSM support
\item Add the GFS\_v17p8, HRRR, RRFS\_v1beta, and WoFS\_v0 suites 
\item Update the vertical coordinate code to better match latest FV3 vertical coordinate code
\item Simplify the case configuration namelists
\item Add greater flexibility for output location (outside of bin directory)
\end{itemize}

\subsection{Limitations}

This release bundle has some known limitations:

\begin{itemize}
\item In the output file, temperature tendency variables all mistakenly have the same description, although their variable names are correct. This has been fixed in the development code.
\item Using the RRFS\_v1beta, HRRR, and WoFS\_v0 suites for cases where deep convection is expected to be active will likely produce strange/unreliable results, unless the forcing has been modified to account for the deep convection. This is because forcing for existing cases assumes a horizontal scale for which deep convection is subgrid-scale and is expected to be parameterized. The  suites without convection are intended for use with regional UFS simulations with horizontal scale small enough not to need a deep convection parameterization active, and it does not contain a deep convective scheme. Nevertheless, these suites are included with the SCM as-is for research purposes.
\item The provided cases over land points cannot use an LSM at this time due to the lack of initialization data for the LSMs. Therefore, for the provided cases over land points (ARM\_SGP\_summer\_1997\_* and LASSO\_*, where sfc\_type = 1 is set in the case configuration file), prescribed surface fluxes must be used:
\begin{itemize}
\item surface sensible and latent heat fluxes must be provided in the case data file
\item sfc\_flux\_spec must be set to true in the case configuration file
\item the surface roughness length in cm must be set in the case configuration file
\item the suite defintion file used (physics\_suite variable in the case configuration file) must have been modified to use prescribed surface fluxes rather than an LSM.
\item NOTE: If one can develop appropriate initial conditions for the LSMs for the supplied cases over land points, there should be no technical reason why they cannot be used with LSMs, however.
\end{itemize}
\item As of this release, using the SCM over a land point with an LSM is possible through the use of UFS initial conditions (see section \ref{sec:UFS ICs}). However, advective forcing terms are unavailable as of this release, so only short integrations using this configuration should be employed. Using dynamical tendencies (advective forcing terms) from the UFS will be part of a future release.
\item There are several capabilities of the developmental code that have not been tested sufficiently to be considered part of the supported release. Those include additional parameterizations. Users that want to use experimental capabilities should refer to Subsection \ref{section: development_code}.
\end{itemize}
