\chapter{Cases}
\label{chapter: cases}

\section{How to run cases}
Only two files are needed to set up and run a case with the SCM. The first is a configuration namelist file found in \execout{ccpp-scm/scm/etc/case\_config} that contains parameters for the SCM infrastructure. The second necessary file is a NetCDF file containing data to initialize the column state and time-dependent data to force the column state. The two files are described below.

\subsection{Case configuration namelist parameters}
\label{subsection: case config}
The \execout{case\_config} namelist expects the following parameters:
\begin{itemize}
\item \execout{case\_name}
	\begin{itemize}
	\item Identifier for which dataset (initialization and forcing) to load. This string must correspond to a dataset included in the directory \execout{ccpp-scm/scm/data/processed\_case\_input/} (without the file extension).
	\end{itemize}
\item \execout{runtime}
	\begin{itemize}
	\item Specify the model runtime in seconds (integer). This should correspond with the forcing dataset used. If a runtime is specified that is longer than the supplied forcing, the forcing is held constant at the last specified values.
	\end{itemize}
\item \execout{thermo\_forcing\_type}
	\begin{itemize}
	\item An integer representing how forcing for temperature and moisture state variables is applied (1 $=$ total advective tendencies, 2 $=$ horizontal advective tendencies with prescribed vertical motion, 3 $=$ relaxation to observed profiles with vertical motion prescribed)
	\end{itemize}
\item \execout{mom\_forcing\_type}
	\begin{itemize}
	\item An integer representing how forcing for horizontal momentum state variables is applied (1 $=$ total advective tendencies; not implemented yet, 2 $=$ horizontal advective tendencies with prescribed vertical motion, 3 $=$ relaxation to observed profiles with vertical motion prescribed)
	\end{itemize}
\item \execout{relax\_time}
	\begin{itemize}
	\item A floating point number representing the timescale in seconds for the relaxation forcing (only used if \execout{thermo\_forcing\_type} $=$ \exec{3} or \execout{mom\_forcing\_type} $=$ \exec{3})
	\end{itemize}
\item \execout{sfc\_flux\_spec}
	\begin{itemize}
	\item A boolean set to \exec{.true.} if surface flux are specified from the forcing data (there is no need to have surface schemes in a suite definition file if so)
	\end{itemize}
\item \execout{sfc\_roughness\_length\_cm}
	\begin{itemize}
	\item Surface roughness length in cm for calculating surface-related fields from specified surface fluxes (only used if \execout{sfc\_flux\_spec} is True).
	\end{itemize}
\item \execout{sfc\_type}
	\begin{itemize}
	\item An integer representing the character of the surface (0 $=$ sea surface, 1 $=$ land surface, 2 $=$ sea-ice surface)
	\end{itemize}
\item \execout{reference\_profile\_choice}
	\begin{itemize}
	\item An integer representing the choice of reference profile to use above the supplied initialization and forcing data (1 $=$ ``McClatchey'' profile, 2 $=$ mid-latitude summer standard atmosphere)
	\end{itemize}
\item \execout{year}
	\begin{itemize}
	\item An integer representing the year of the initialization time
	\end{itemize}
\item \execout{month}
	\begin{itemize}
	\item An integer representing the month of the initialization time
	\end{itemize}
\item \execout{day}
	\begin{itemize}
	\item An integer representing the day of the initialization time
	\end{itemize}
\item \execout{hour}
	\begin{itemize}
	\item An integer representing the hour of the initialization time
	\end{itemize}
\item \execout{column\_area}
	\begin{itemize}
	\item A list of floating point values representing the characteristic horizontal domain area of each atmospheric column in square meters (this could be analogous to a 3D model's horizontal grid size or the characteristic horizontal scale of an observation array; these values are used in scale-aware schemes; if using multiple columns, you may specify an equal number of column areas)
	\end{itemize}
\item \execout{model\_ics}
	\begin{itemize}
	\item A boolean set to \exec{.true.} if UFS atmosphere initial conditions are used rather than field campaign-based initial conditions
	\end{itemize}
\item \execout{C\_RES}
	\begin{itemize}
	\item An integer representing the grid size of the UFS atmosphere initial conditions; the integer represents the number of grid points in each horizontal direction of each cube tile
	\end{itemize}
\item \execout{input\_type}
        \begin{itemize}
        \item  0 => original DTC format, 1 => DEPHY-SCM format.
        \end{itemize}
\end{itemize}

Optional variables (that may be overridden via run script command line arguments) are:
\begin{itemize}
\item \execout{vert\_coord\_file}
        \begin{itemize}
          \item File containing FV3 vertical grid coefficients.
        \end{itemize}
\item \execout{n\_levels}
	\begin{itemize}
	\item Specify the integer number of vertical levels.
	\end{itemize}
\end{itemize}

\subsection{Case input data file (CCPP-SCM format)}
\label{subsection: case input}

The initialization and forcing data for each case is stored in a NetCDF (version 4) file within the \execout{ccpp-scm/scm/data/processed\_case\_input} directory. Each file has at least two dimensions (\execout{time} and \execout{levels}, potentially with additions for vertical snow and soil levels) and is organized into 3 groups: scalars, initial, and forcing. Not all fields are required for all cases. For example the fields \execout{sh\_flux\_sfc} and \execout{lh\_flux\_sfc} are only needed if the variable \execout{sfc\_flx\_spec} $=$ \exec{.true.} in the case configuration file and state nudging variables are only required if \execout{thermo\_forcing\_type} $=$ \exec{3} or \execout{mom\_forcing\_type} $=$ \exec{3}. Using an active LSM (Noah, NoahMP, RUC) requires many more variables than are listed here. Example files for using with Noah and NoahMP LSMs are included in \execout{ccpp-scm/scm/data/processed\_case\_input/fv3\_model\_point\_noah[mp].nc}.

\lstinputlisting[
                 basicstyle=\scriptsize\ttfamily,
                 label=lst_case_input_netcdf_header,
                 caption=example NetCDF file (CCPP-SCM format) header for case initialization and forcing data
                 ]{./arm_case_header.txt}

\subsection{Case input data file (DEPHY format)}
\label{subsection: case input dephy}
The Development and Evaluation of Physics in atmospheric models (DEPHY) format is an internationally-adopted data format intended for use by SCM and LESs. The initialization and forcing data for each case is stored in a NetCDF (version 4) file, although these files are not by default included in the CCPP SCM repository. To access these cases you need to clone the DEPHY-SCM repository, and provide the DEPHY-SCM file location to the SCM. For example:
\begin{lstlisting}[language=bash]
cd [...]/ccpp-scm/scm/data
git clone https://github.com/GdR-DEPHY/DEPHY-SCM DEPHY-SCM
cd [...]/ccpp-scm/scm/bin
./run_scm.py -c MAGIC_LEG04A --case_data_dir [...]/ccpp-scm/scm/data/DEPHY-SCM/MAGIC/LEG04A -v
\end{lstlisting}
Each DEPHY file has three dimensions (\execout{time}, \execout{t0}, \execout{levels}) and contains the initial conditions (\execout{t0}, \execout{levels}) and forcing data (\execout{time}, \execout{levels}). Just as when using the CCPP-SCM formatted inputs, \ref{subsection: case input}, not all fields are required for all cases. More information on the DEPHY format requirements can be found at \href{https://github.com/GdR-DEPHY/DEPHY-SCM}{DEPHY}. 

\lstinputlisting[
                 basicstyle=\scriptsize\ttfamily,
                 label=lst_case_input_netcdf_header,
                 caption=example NetCDF file (DEPHY format) header for case initialization and forcing data
                 ]{./dephy_case_header.txt}

\section{Included Cases}
Several cases are included in the repository to serve as examples for users to create their own and for basic research. All case configuration namelist files for included cases can be found in \execout{ccpp-scm/scm/etc/case\_config} and represent the following observational field campaigns:
\begin{itemize}
\item Tropical Warm Pool -- International Cloud Experiment (TWP-ICE) maritime deep convection
\item Atmospheric Radiation Measurement (ARM) Southern Great Plains (SGP) Summer 1997 continental deep convection
\item Atlantic Stratocumulus Transition EXperiment (ASTEX) maritime stratocumulus-to-cumulus transition
\item Barbados Oceanographic and Meteorological EXperiment (BOMEX) maritime shallow convection
\item Large eddy simulation ARM Symbiotic Simulation and Observation (LASSO) for May 18, 2016 (with capability to run all LASSO dates - see \ref{sec:lasso}) continental shallow convection
\end{itemize}
For the ARM SGP case, several case configuration files representing different time periods of the observational dataset are included, denoted by a trailing letter. The LASSO case may be run with different forcing applied, so three case configuration files corresponding to these different forcing are included. In addition, two example cases are included for using UFS Atmosphere initial conditions:
\begin{itemize}
\item UFS initial conditions for 38.1 N, 98.5 W (central Kansas) for 00Z on Oct. 3, 2016 with Noah variables on the C96 FV3 grid (\execout{fv3\_model\_point\_noah.nc})
\item UFS initial conditions for 38.1 N, 98.5 W (central Kansas) for 00Z on Oct. 3, 2016 with NoahMP variables on the C96 FV3 grid (\execout{fv3\_model\_point\_noahmp.nc})
\end{itemize}
See \ref{sec:UFSreplay} for information on how to generate these files for other locations and dates, given appropriate UFS Atmosphere initial conditions and output.

\section{How to set up new cases}

Setting up a new case involves preparing the two types of files listed above. For the case initialization and forcing data file, this typically involves writing a custom script or program to parse the data from its original format to the format that the SCM expects, listed above. An example of this type of script written in Python is included in \execout{/ccpp-scm/scm/etc/scripts/twpice\_forcing\_file\_generator.py}. The script reads in the data as supplied from its source, converts any necessary variables, and writes a NetCDF (version 4) file in the format described in subsections \ref{subsection: case input} and \ref{subsection: case input dephy}. For reference, the following formulas are used:
\begin{equation}
\theta_{il} = \theta - \frac{\theta}{T}\left(\frac{L_v}{c_p}q_l + \frac{L_s}{c_p}q_i\right)
\end{equation}
\begin{equation}
q_t = q_v + q_l + q_i
\end{equation}
where $\theta_{il}$ is the ice-liquid water potential temperature, $\theta$ is the potential temperature, $L_v$ is the latent heat of vaporization, $L_s$ is the latent heat of sublimation $c_p$ is the specific heat capacity of air at constant pressure, $T$ is absolute temperature, $q_t$ is the total water specific humidity, $q_v$ is the water vapor specific humidity, $q_l$ is the suspended liquid water specific humidity, and $q_i$ is the suspended ice water specific humidity.

As shown in the example NetCDF header, the SCM expects that the vertical dimension is pressure levels (index 1 is the surface) and the time dimension is in seconds. The initial conditions expected are the height of the pressure levels in meters, and arrays representing vertical columns of $\theta_{il}$ in K, $q_t$, $q_l$, and $q_i$ in kg kg$^{-1}$, $u$ and $v$ in m s$^{-1}$, turbulence kinetic energy in m$^2$ s$^{-2}$ and ozone mass mixing ratio in kg kg$^{-1}$.

For forcing data, the SCM expects a time series of the following variables: latitude and longitude in decimal degrees [in case the column(s) is moving in time (e.g., Lagrangian column)], the surface pressure (Pa) and surface temperature (K). If surface fluxes are specified for the new case, one must also include a time series of the kinematic surface sensible heat flux (K m s$^{-1}$) and kinematic surface latent heat flux (kg kg$^{-1}$ m s$^{-1}$). The following variables are expected as 2-dimensional arrays (vertical levels first, time second):  the geostrophic u (E-W) and v (N-S) winds (m s$^{-1}$), and the horizontal and vertical advective tendencies of $\theta_{il}$ (K s$^{-1}$) and $q_t$ (kg kg$^{-1}$ s$^{-1}$), the large scale vertical velocity (m s$^{-1}$), large scale pressure vertical velocity (Pa s$^{-1}$), the prescribed radiative heating rate (K s$^{-1}$), and profiles of u, v, T, $\theta_{il}$ and $q_t$ to use for nudging.

Although it is expected that all variables are in the NetCDF file, only those that are used with the chosen forcing method are required to be nonzero. For example, the following variables are required depending on the values of \execout{mom\_forcing\_type} and \execout{thermo\_forcing\_type} specified in the case configuration file:

\begin{itemize}
\item \execout{mom\_forcing\_type} $=$ \exec{1}
	\begin{itemize}
		\item Not implemented yet
	\end{itemize}
\item \execout{mom\_forcing\_type} $=$ \exec{2}
	\begin{itemize}
		\item geostrophic winds and large scale vertical velocity
	\end{itemize}
\item \execout{mom\_forcing\_type} $=$ \exec{3}
	\begin{itemize}
		\item u and v nudging profiles
	\end{itemize}
\item \execout{thermo\_forcing\_type} $=$ \exec{1}
	\begin{itemize}
		\item horizontal and vertical advective tendencies of $\theta_{il}$ and $q_t$ and prescribed radiative heating (can be zero if radiation scheme is active)
	\end{itemize}
\item \execout{thermo\_forcing\_type} $=$ \exec{2}
	\begin{itemize}
		\item horizontal advective tendencies of $\theta_{il}$ and $q_t$, prescribed radiative heating (can be zero if radiation scheme is active), and the large scale vertical pressure velocity
	\end{itemize}
\item \execout{thermo\_forcing\_type} $=$ \exec{3}
	\begin{itemize}
		\item $\theta_{il}$ and $q_t$ nudging profiles and the large scale vertical pressure velocity
	\end{itemize}
\end{itemize}

For the case configuration file, it is most efficient to copy an existing file in \execout{ccpp-scm/scm/etc/case\_config} and edit it to suit one's case. Recall from subsection \ref{subsection: case config} that this file is used to configure the SCM framework parameters for a given case. Be sure to check that model timing parameters such as the time step and output frequency are appropriate for the physics suite being used. There is likely some stability criterion that governs the maximum time step based on the chosen parameterizations and number of vertical levels (grid spacing). The \execout{case\_name} parameter should match the name of the case input data file that was configured for the case (without the file extension). The \execout{runtime} parameter should be less than or equal to the length of the forcing data unless the desired behavior of the simulation is to proceed with the last specified forcing values after the length of the forcing data has been surpassed. The initial date and time should fall within the forcing period specified in the case input data file. If the case input data is specified to a lower altitude than the vertical domain, the remainder of the column will be filled in with values from a reference profile. There is a tropical profile and mid-latitude summer profile provided, although one may add more choices by adding a data file to \execout{ccpp-scm/scm/data/processed\_case\_input} and adding a parser section to the subroutine \execout{get\_reference\_profile} in \execout{-scm/scm/src/scm\_input.f90}. Surface fluxes can either be specified in the case input data file or calculated using a surface scheme using surface properties. If surface fluxes are specified from data, set \execout{sfc\_flux\_spec} to \exec{.true.} and specify \execout{sfc\_roughness\_length\_cm} for the surface over which the column resides. Otherwise, specify a \execout{sfc\_type}. In addition, one must specify a \execout{column\_area} for each column.

To control the forcing method, one must choose how the momentum and scalar variable forcing are applied. The three methods of Randall and Cripe (1999, JGR) have been implemented: ``revealed forcing'' where total (horizontal $+$ vertical) advective tendencies are applied (type 1), ``horizontal advective forcing'' where horizontal advective tendencies are applied and vertical advective tendencies are calculated from a prescribed vertical velocity and the calculated (modeled) profiles (type 2), and ``relaxation forcing'' where nudging to observed profiles replaces horizontal advective forcing combined with vertical advective forcing from prescribed vertical velocity (type 3). If relaxation forcing is chosen, a \execout{relax\_time} that represents the timescale over which the profile would return to the nudging profiles must be specified.

\section{Using other LASSO cases}
\label{sec:lasso}

In order to use other LASSO cases than the one provided, perform the following steps:
\begin{enumerate}
\item Access \url{http://archive.arm.gov/lassobrowser} and use the navigation on the left to choose the dates for which you would like to run a SCM simulation. Pay attention to the ``Large Scale Forcing'' tab where you can choose how the large scale forcing was generated, with options for ECMWF, MSDA, and VARANAL. All are potentially valid, and it is likely worth exploring the differences among forcing methods. Click on Submit to view a list of simulations for the selected criteria. Choose from the simulations (higher skill scores are preferred) and check the ``Config Obs Model Tar'' box to download the data. Once the desired simulations have been checked, order the data (you may need to create an ARM account to do so).
\item Once the data is downloaded, decompress it. From the \execout{config} directory, copy the files \execout{input\_ls\_forcing.nc}, \execout{input\_sfc\_forcing.nc}, and \execout{wrfinput\_d01.nc} into their own directory under \execout{ccpp-scm/scm/data/raw\_case\_input/}.
\item Modify \execout{ccpp-scm/scm/etc/scripts/lasso1\_forcing\_file\_generator\_gjf.py} to point to the input files listed above. Execute the script in order to generate a case input file for the SCM (to be put in \execout{ccpp-scm/scm/data/processed\_case\_input/}):
\begin{lstlisting}[language=bash]
./lasso1_forcing_file_generator_gjf.py
\end{lstlisting}
\item Create a new case configuration file (or copy and modify an existing one) in \execout{ccpp-scm/scm/etc/case\_config}. Be sure that the \execout{case\_name} variable points to the newly created/processed case input file from above.
\end{enumerate}

\section{Using UFS Output to Create SCM Cases: UFS-Replay}
\label{sec:UFSreplay}


\subsection{Python Dependencies}
\label{subsection: pydepend}
The scripts here require a few python packages that may not be found by default in all python installations. There is a YAML file with the python environment needed to run the script in \execout{ccpp-scm/environment-ufsreplay.yml}. To create and activate this environment using conda:

Create environment (only once):

\execout{> conda env create -f environment-ufsreplay.yml}

This will create the conda environment \execout{env\_ufsreplay}


Activate environment:

\execout{> conda activate env\_ufsreplay}


\subsection{UFS\_IC\_generator.py}
\label{subsection: ufsicgenerator}
A script exists in \execout{scm/etc/scripts/UFS\_IC\_generator.py} to read in UFS history (output) files and their initial conditions to generate a SCM case input data file, in DEPHY format. 


\begin{lstlisting}[language=bash]
./UFS_IC_generator.py [-h] (-l LOCATION LOCATION | -ij INDEX INDEX) -d
DATE -i IN_DIR -g GRID_DIR -f FORCING_DIR -n
CASE_NAME [-t {1,2,3,4,5,6,7}] [-a AREA] [-oc]
[-lam] [-sc] [-near]
\end{lstlisting}

Mandatory arguments:
\begin{enumerate}
\item \exec{-{}-location (-l)} OR \exec{-{}-index (-ij)}:  Either longitude and latitude in decimal degrees east and north of a location OR the UFS grid index with the tile number
	\begin{itemize}
		\item -l 261.51 38.2 (two floating point values separated by a space)
		\item -ij 8 49 (two integer values separated by a space; this option must also use the \exec{-{}-tile (-t)} argument to specify the tile number)
	\end{itemize}
\item \exec{-{}-date (-d)} YYYYMMDDHHMMSS: date corresponding to the UFS initial conditions
\item \exec{-{}-in\_dir (-i)}: path to the directory containing the UFS initial conditions
\item \exec{-{}-grid\_dir (-g)}: path to the directory containing the UFS supergrid files (AKA "fix" directory)
\item \exec{-{}-forcing\_dir (-f)}: path to the directory containing the UFS history files
\item \exec{-{}-case\_name (-n)}: name of case
\end{enumerate}

Optional arguments:
\begin{enumerate}
\item \exec{-{}-tile (-t)}: if one already knows the correct tile for the given longitude and latitude OR one is specifying the UFS grid index (\exec{-{}-index} argument)
\item \exec{-{}-area (-a)}: area of grid cell in $m^2$ (if known or different than the value calculated from the supergrid file)
\item \exec{-{}-old\_chgres (-oc)}: flag if UFS initial conditions were generated using older version of chgres (global\_chgres); might be the case for pre-2018 data
\item \exec{-{}-lam (-lam)}: flag to signal that the ICs and forcing is from a limited-area model run
\item \exec{-{}-save\_comp (-sc)}: flag to create UFS reference file for comparison
\item \exec{-{}-use\_nearest (-near)}: flag to indicate using the nearest UFS history file gridpoint
\end{enumerate}

\subsection{UFS\_forcing\_ensemble\_generator.py}
\label{subsection: ufsforcingensemblegenerator}
There is an additional script in \execout{scm/etc/scripts/UFS\_forcing\_ensemble\_generator.py} to create UFS-replay case(s) starting with output from UFS Weather Model (UWM) Regression Tests (RTs).

\begin{lstlisting}[language=bash]
UFS_forcing_ensemble_generator.py [-h] -d DIR -n CASE_NAME
(-lonl LON_1 LON_2 -latl LAT_1 LAT_2 -nens NENSMEMBERS |
-lons [LON_LIST] -lats [LAT_LIST])
[-dt TIMESTEP] [-cres C_RES] [-sdf SUITE] [-sc] [-near]
\end{lstlisting}

Mandatory arguments:
\begin{enumerate}
\item \exec{-{}-dir (-d)}: path to UFS Regression Test output
\item \exec{-{}-case\_name (-n)}: name of cases
\item Either: (see examples below) 
      \begin{itemize}
           \item \exec{-{}-lon\_limits (-lonl)} AND \exec{-{}-lat\_limits (-latl)} AND \exec{-{}-nensmembers (-nens)}: longitude range, latitude range, and number of cases to create
           \item \exec{-{}-lon\_list (-lons)} AND \exec{-{}-lat\_list (-lats)}: longitude and latitude of cases
      \end{itemize}
\end{enumerate}

Optional arguments:
\begin{enumerate}
\item \exec{-{}-timestep (-dt)}: SCM timestep, in seconds
\item \exec{-{}-C\_res (-cres)}: UFS spatial resolution
\item \exec{-{}-suite (-sdf)}: CCPP suite definition file to use for ensemble
\item \exec{-{}-save\_comp (-sc)}: flag to create UFS reference file for comparison
\item \exec{-{}-use\_nearest (-near)}: flag to indicate using the nearest UFS history file gridpoint
\end{enumerate}

Examples to run from within the \exec{scm/etc/scripts} directory to create SCM cases starting with the output from a UFS Weather Model regression test(s):

On the supported platforms Cheyenne (NCAR) and Hera (NOAA), there are staged UWM RTs located at:
\begin{itemize}
\item \execout{Cheyenne /glade/scratch/epicufsrt/GMTB/CCPP-SCM/UFS\_RTs}
\item \execout{Hera /scratch1/BMC/gmtb/CCPP-SCM/UFS\_RTs}
\end{itemize}

\subsection{Example 1: UFS-replay for single point}
\label{subsection: example1}

UFS regression test, \execout{control\_c192}, for single point.
\begin{lstlisting}[language=bash]
./UFS_forcing_ensemble_generator.py -d /glade/scratch/epicufsrt/GMTB/CCPP-SCM/UFS_RTs/control_c192/ -sc --C_RES 192 -dt 360  -n control_c192 -lons 300 -lats 34
\end{lstlisting}

Upon successful completion of the script, the command to run the case(s) will print to the screen. For example,

\begin{lstlisting}[language=bash]
./run_scm.py --npz_type gfs --file scm_ufsens_control_c192.py --timestep 360
\end{lstlisting}

The file \exec{scm\_ufsens\_control\_c192.py} is created in \exec{ccpp-scm/scm/bin/}, where the SCM run script is to be exectued.

\subsection{Example 2: UFS-replay for list of points}
\label{subsection: example2}

UFS regression test, \execout{control\_c384}, for multiple points.
\begin{lstlisting}[language=bash]
./UFS_forcing_ensemble_generator.py -d /glade/scratch/epicufsrt/GMTB/CCPP-SCM/UFS_RTs/control_c384/ -sc --C_RES 384 -dt 225 -n control_c384 -lons 300 300 300 300 -lats 34 35 35 37
\end{lstlisting}

Upon successful completion of the script, the command to run the case(s) will print to the screen. For example,

\begin{lstlisting}[language=bash]
./run_scm.py --npz_type gfs --file scm_ufsens_control_c384.py --timestep 225
\end{lstlisting}

The file \exec{scm\_ufsens\_control\_c384.py} contains \exec{ALL} of the cases created. Each case created will have the naming convention \exec{case\_name\_nXXX}, where the suffix \exec{XXX} is the case number from 0 to the number of points provided. The contents of the file should look like:
\begin{lstlisting}[language=bash]
run_list = [{"case": "control_c384_n000", "suite": "SCM_GFS_v16"},
            {"case": "control_c384_n001", "suite": "SCM_GFS_v16"},
            {"case": "control_c384_n002", "suite": "SCM_GFS_v16"},
            {"case": "control_c384_n003", "suite": "SCM_GFS_v16"}]
\end{lstlisting}

\subsection{Example 3: UFS-replay for an ensemble of points}
\label{subsection: example3}

UFS regression test, \execout{control\_p8}, for an ensemble (10) of randomly selected points over a specified longitude ($300-320^oW$) and latitude ($40-50^oN$) range

But first, to use the \execout{control\_p8} test we need to rerun the regression test to generate UFS history files with a denser and constant output interval. First, in \execout{control\_p8/model\_configure}, change \exec{-{}-output\_fh} to \execout{"interval -1"}, where \execout{interval} is the UFS history file output frequency (in hours), see \href{https://ufs-weather-model.readthedocs.io/en/latest/InputsOutputs.html}{UFS Weather Model Users Guide} for more details.

For the purposes of this example the \execout{control\_p8} test has already been rerun, but if starting from your own UWM RTs, you can rerun the UWM regression test, on Cheyenne for example, by running the following command in the RT directory: \execout{qsub job\_card}

Now the cases can be generated with the following command:
\begin{lstlisting}[language=bash]
./UFS_forcing_ensemble_generator.py -d /glade/scratch/epicufsrt/GMTB/CCPP-SCM/UFS_RTs/control_p8/ -sc --C_RES 96 -dt 720 -n control_p8 -lonl 300 320 -latl 40 50 -nens 10 -sdf SCM_GFS_v17_p8
\end{lstlisting}

Upon successful completion of the script, the command to run the case(s) will print to the screen. For example,

\begin{lstlisting}[language=bash]
./run_scm.py --npz_type gfs --file scm_ufsens_control_p8.py --timestep 720
\end{lstlisting}

The file \exec{scm\_ufsens\_control\_p8.py} contains ten cases (n000-n009) to be run. The contents of the file should look like:
\begin{lstlisting}[language=bash]
run_list = [{"case": "control_p8_n000", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n001", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n002", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n003", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n004", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n005", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n006", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n007", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n008", "suite": "SCM_GFS_v17_p8"},
            {"case": "control_p8_n009", "suite": "SCM_GFS_v17_p8"}]
\end{lstlisting}
