\chapter{Repository}
\label{chapter: repository}

\section{What is included in the repository?}
The repository contains all code and data required to run the GMTB SCM. It is functionally separated into 4 subdirectories representing the SCM model infrastructure (\execout{scm} directory), the CCPP infrastructure (\execout{ccpp-framework} directory), the CCPP physics schemes (\execout{ccpp-physics} directory), and any necessary external library code (\execout{external} directory). The entire \execout{gmtb-scm} repository resides on Github's NCAR account, and the \execout{ccpp-framework} and \execout{ccpp-physics} directories are git submodules that point to repositories on the same account. Note, to facilitate the public release, the gmtb-scm-release repository also includes the ccpp-framework and ccpp-physics codes, so users do not have to obtain those as submodules. The structure of the entire repository is represented below. Note that the \execout{ccpp\_physics} repository contains files needed for using the CCPP with the experimental version of the Global Forecast System (GFS) that uses the Finite-Volume Cubed-Sphere (FV3) model (FV3GFS), even though the use of CCPP with FV3GFS is not supported in this release.

{\small\justify
\dirtree{%
	.1 gmtb-scm/.
	.2 ccpp-framework/.
	.3 cmake/\DTcomment{custom cmake code for building ccpp-framework}.
	.3 CMakeLists.txt\DTcomment{cmake configuration file for ccpp-framework}.
	.3 doc/\DTcomment{doxygen configuration, output, and Developer's Guide}.
	.3 LICENSE.
	.3 README.md.
	.3 schemes/\DTcomment{contains schemes used for testing}.
	.3 scripts/\DTcomment{contains ccpp\_prebuild and other python scripts for parsing metadata}.
	.3 src/\DTcomment{contains CCPP framework code}.
	.3 suites/\DTcomment{contains suite definition files and XML schema definition files}.
	.2 ccpp-physics/\DTcomment{contains all physics schemes}.
	.3 CCPP\_CAPS.cmake\DTcomment{auto-generated cmake section for physics caps}.
	.3 CCPP\_CAPS.mk\DTcomment{auto-generated makefile section for physics caps}.
	.3 CCPP\_schemes.cmake\DTcomment{auto-generated cmake section for physics schemes}.
	.3 CCPP\_schemes.mk\DTcomment{auto-generated makefile section for physics schemes}.
	.3 CMakeLists.txt\DTcomment{cmake configuration file for ccpp-physics}.
	.3 LICENSE.
	.3 pgifix.py.
	.3 physics/\DTcomment{contains all CCPP physics and interstitial schemes}.
	.4 docs/\DTcomment{contains CCPP physics doxygen documentation}.
	.3 stochastic\_physics\DTcomment{contains all stochastic physics code - FV3 only for now}.
	.3 README.md.
	.2 external/.
	.3 bacio\DTcomment{NCEP library bacio (needed for GFS physics)}.
	.3 sp\DTcomment{NCEP library sp (needed for GFS physics)}.
	.3 w3nco\DTcomment{NCEP library w3 (needed for GFS physics and SCM infrastructure)}.
	.2 scm/.
	.3 bin/\DTcomment{build directory (initially empty; populated by cmake)}.
	.3 data/.
	.4 comparison\_data/\DTcomment{contains data with which to compare SCM output}.
	.4 GFS\_physics\_data/\DTcomment{contains data needed by the GFS physics suite}.
	.4 processed\_case\_input/\DTcomment{contains initialization and forcing data for cases}.
	.4 raw\_case\_input/\DTcomment{contains case data to be processed by scripts}.
	.4 vert\_coord\_data/\DTcomment{contains data to calculate vertical coordinates}.
	.3 doc/\DTcomment{contains doxygen configuration file, images, and output}.
	.4 html/\DTcomment{contains HTML output from doxygen}.
	.4 README\_MACOSX.txt.
	.4 README\_UBUNTU.txt.
	.4 README\_CENTOS.txt.
	.5 TechGuide/\DTcomment{contains LaTeX for this User's Guide}.
	.3 etc/\DTcomment{contains case configuration, machine setup scripts, and plotting scripts}.
	.4 case\_config/\DTcomment{contains case configuration files and physics namelist files}.
	.4 CENTOS\_setup.csh\DTcomment{setup script for CentOS Linux for csh, tcsh}.
	.4 CENTOS\_setup.sh\DTcomment{setup script for CentOS Linux for sh, bash}.
	.4 Cheyenne\_setup\_gnu.csh\DTcomment{setup script for Cheyenne HPC for csh, tcsh}.
	.4 Cheyenne\_setup\_gnu.sh\DTcomment{setup script for Cheyenne HPC for sh, bash}.
	.4 Cheyenne\_setup\_intel.csh\DTcomment{setup script for Cheyenne HPC for csh, tcsh}.
	.4 Cheyenne\_setup\_intel.sh\DTcomment{setup script for Cheyenne HPC for sh, bash}.
	.4 Cheyenne\_setup\_pgi.csh\DTcomment{setup script for Cheyenne HPC for csh, tcsh}.
	.4 Cheyenne\_setup\_pgi.sh\DTcomment{setup script for Cheyenne HPC for sh, bash}.
	.4 gmtb\_scm\_run.py\DTcomment{example QSUB run script}.
	.4 MACOSX\_setup.csh\DTcomment{setup script for Mac OS X for csh, tcsh}.
	.4 MACOSX\_setup.sh\DTcomment{setup script for Mac OS X for sh, bash}.
	.4 scripts/\DTcomment{python scripts for setting up cases and plotting}.
	.5 f90nml.0.19/\DTcomment{f90nml python package}.
	.5 plot\_configs/\DTcomment{plot configuration files}.
	.4 Theia\_setup\_gnu.csh\DTcomment{setup script for Theia HPC for csh, tcsh}.
	.4 Theia\_setup\_gnu.sh\DTcomment{setup script for Theia HPC for sh, bash}.
	.4 Theia\_setup\_intel.csh\DTcomment{setup script for Theia HPC for csh, tcsh}.
	.4 Theia\_setup\_intel.sh\DTcomment{setup script for Theia HPC for sh, bash}.
	.4 Theia\_setup\_pgi.csh\DTcomment{setup script for Theia HPC for csh, tcsh}.
	.4 Theia\_setup\_pgi.sh\DTcomment{setup script for Theia HPC for sh, bash}.
	.4 UBUNTU\_setup.csh\DTcomment{setup script for Ubuntu Linux for csh, tcsh}.
	.4 UBUNTU\_setup.sh\DTcomment{setup script for Ubuntu Linux for sh, bash}.
	.3 LICENSE.txt.
	.3 src/\DTcomment{source code for SCM infrastructure}.
	.4 cmake/\DTcomment{contains custom FindNetCDF.cmake}.
}}
